Feature importance analysis

### 2020-04-18 analysis/feature-importance.Rmd
wflow_publish(knitr_in("analysis/feature-importance.Rmd"), view = FALSE,     verbose = TRUE)

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

>>>>

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```
